### 2017-03-14 thesis/results/results.tex
Added all of the extra results in appendix2; clean up the titles - tmp commit
Draft thesis completed; now edit the whole thing - tmp commit

\begin{figure}[htb]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/creighton_mg_heatmap1}
	\caption[Obesity metagene from \citet{Creighton2012} study and sample gene expression in CR data]{Heatmap showing the obesity metagene from the \citet{Creighton2012} study with the gene expressions of obesity associated genes in CR data.
	Level of expression is represented in the top right histogram, where low and high gene expression were colour-coded with blue and red, respectively.
	Each row of the heatmap represents a gene from the obesity associated genetic signature, and each column of the heatmap represents a sample from CR data.
	The obesity associated metagene scores of the samples are shown in a separate row at top of the heatmap, and the tree diagram of the heirarchical clustering of the genes is shown to the left of the heatmap.
	For clarity, the metagene scores were flipped in order to match the results from the \citet{Creighton2012} study.}
	\label{fig:crmetaheat}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=4,width=0.45\linewidth]{results1/creighton_mg_heatmap1}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/creighton_mg_heatmap1}
	\caption[Obesity metagene from the \citet{Creighton2012} study and sample \gls{bmi}/\gls{bmi} status in CR data]{Box plot and scatter plot showing the association of the obesity metagene from the \citet{Creighton2012} study with sample \gls{bmi} status and \gls{bmi} from CR data, respectively.
	In the box plot, the p-values above the groups represent the statistical significance of the association of the metagene with the overweight or obese group compared with the normal weight group.
	The \gls{anova} p-value shows the statistical significance of the association of the metagene with the sample \gls{bmi} groups.
	In the scatter plot, $R^2$- and p-values describe the adjusted coefficient of determination of the regression line and the statistical significance of the linear model used to draw the regression line, respectively.}
	\label{fig:crmetaboxplot}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/crtcga_std}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/crtcga_std}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/crtcga_std}
	\caption[Obesity metagene from the \citet{Creighton2012} study in \acrshort{icgc} \acrshort{blca} data]{Heatmap, box plot and scatter plot showing the association of obesity metagene from the \citet{Creighton2012} study with sample gene expression, \gls{bmi} and \gls{bmi} status from \gls{icgc} \gls{blca} data, respectively.
	The results for other cancer types are in \cref{app:a}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:crmetaicgc}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.8\linewidth,page=3]{results1/cris_cr_trans_meta}\\
	\vspace{1em}
	\includegraphics[width=0.45\linewidth,page=4]{results1/cris_cr_trans_meta}
	\hfill
	\includegraphics[width=0.45\linewidth,page=5]{results1/cris_cr_trans_meta}
	\caption[Obesity metagene from \citet{Creighton2012} study in \gls{nzbc} data]{Heatmap, box plot and scatter plot showing the association of obesity metagene from the \citet{Creighton2012} study with sample gene expression, \gls{bmi} and \gls{bmi} status from \gls{nzbc} data, respectively.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:crmetaprint}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cr_fm_meta}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cr_fm_meta}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cr_fm_meta}
	\caption[FM metagene in CR data]{Heatmap, box plot and scatter plot showing the association of FM obesity associated metagene with sample gene expression, \gls{bmi} and \gls{bmi} status from CR  data, respectively.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:fmmetacr}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/fm_meta_ICGC}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/fm_meta_ICGC}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/fm_meta_ICGC}
	\caption[FM metagene in \acrshort{icgc} \acrshort{blca} data]{Heatmap, box plot and scatter plot showing the association of FM obesity associated metagene with sample gene expression, \gls{bmi} and \gls{bmi} status from \acrshort{icgc} \acrshort{blca} data, respectively.
	The results for other cancer types are in \cref{app:a}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:fmmetaicgc}
\end{figure}

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cris_fm_meta}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cris_fm_meta}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cris_fm_meta}
	\caption[FM metagene in \gls{nzbc} data]{Heatmap, box plot and scatter plot showing the association of FM obesity associated metagene with sample gene expression, \gls{bmi} and \gls{bmi} status from \gls{nzbc} data, respectively.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:fmmetacris}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.5\linewidth]{results1/deg_venn1}
	\caption[Veen diagram of the \glspl{deg} identified from CR data (all samples)]{Venn diagram showing the common genes between the signatures obtained from unadjusted and clinical variable-adjusted CR data and the original obesity associated genetic signature.}
	\label{fig:venn1}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.5\linewidth]{results1/deg_venn2}
	\caption[Summary of the \glspl{deg} identified from CR data (Caucasian patient data)]{Venn diagram showing the common genes between the signatures obtained from unadjusted and clinical variable-adjusted CR data (Caucasian patients only) and the original obesity associated genetic signature.}
	\label{fig:venn2}
\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption{Summary of the abbreviations used to refer to the different obesity associated genetic signatures}
	\label{tab:mg_abbrev}
	\begin{tabular}{lp{0.51\textwidth}c}
		\hline
		\hline
		Abbreviation & Definition & No. of gene probes\\
		\hline
		\rule{0pt}{2.25ex}Or      & Original obesity associated genetic signature identified by \citet{Creighton2012}                       & 799\\
		\rule{0pt}{2.25ex}Cr      & Obesity associated genetic signature identified from unadjusted CR data                                & 799 \\
		\rule{0pt}{2.25ex}CrOl    & Genes common between Or and Cr genetic signatures                                                       & 239\\
		\rule{0pt}{2.25ex}Res     & Obesity associated genetic signature identified from clinical variable-adjusted CR data                & 799\\
		\rule{0pt}{2.25ex}ResOl   & Genes common between Or and Res genetic signatures                                                      & 168\\
		\rule{0pt}{2.25ex}Ca      & Obesity associated genetic signature identified from unadjusted Caucasian-only CR data                 & 799\\
		\rule{0pt}{2.25ex}CaOl    & Genes common between Or and Ca genetic signatures                                                       & 148\\
		\rule{0pt}{2.25ex}CaRes   & Obesity associated genetic signature identified from clinical variable-adjusted Caucasian-only CR data & 799\\
		\rule{0pt}{2.25ex}CaResOl & Genes common between Or and CaRes genetic signatures                                                    & 92\\
		\hline
		\hline
	\end{tabular}
\end{table}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cr_deg_meta_vs_clin}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cr_deg_meta_vs_clin}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cr_deg_meta_vs_clin}
	\caption[Cr obesity associated metagene in CR data]{Heatmap, box plot and scatter plot showing the association of Cr obesity associated metagene with sample gene expression, \gls{bmi} and \gls{bmi} status from CR data, respectively.
	The results for other metagenes are in \cref{app:a}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:degmetacr}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.8\linewidth]{results1/cr_meta_cor}
	\caption[Pearson correlation of all eight obesity associated metagenes identified in CR data]{Heatmap showing the Pearson correlation of all eight obesity associated metagenes from CR data with one another.
	\gls{svd} was applied to \gls{rma}-normalised CR data to generate each of the eight metagenes.
	High and low correlation were represented as red and blue, respectively, where the colours were matched with the values on the scale shown in top right.}
	\label{fig:cr_meta_cor}
\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption{P-values of all the metagenes in \gls{blca} cancer data}
	\label{tab:degmetablca}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			 Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr & {\bfseries 0.0134}\tnote{1} & 0.1365 & {\bfseries 0.0387} & 0.0171 & {\bfseries 0.0195} \\
			Res                  & {\bfseries 0.0055}          & 0.1974 & {\bfseries 0.0196} & 0.0117 & {\bfseries 0.0446} \\
			CrOl                 & {\bfseries 0.0383}          & 0.4583 & 0.1096             & 0.0047 & 0.1374             \\
			ResOl                & 0.0909                      & 0.7092 & 0.2125             & 0.0018 & 0.2254             \\
			Ca                   & {\bfseries 0.0077}          & 0.1973 & {\bfseries 0.0231} & 0.0116 & {\bfseries 0.0456} \\
			CaRes                & {\bfseries 0.0104}          & 0.2712 & {\bfseries 0.0322} & 0.0101 & 0.0572             \\
			CaOl                 & 0.0575                      & 0.6185 & 0.1487             & 0.0022 & 0.2126             \\
			CaResOl              & {\bfseries 0.0463}          & 0.5820 & 0.1263             & 0.0036 & 0.1660             \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/rawobsgene_ICGC}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/rawobsgene_ICGC}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/rawobsgene_ICGC}
	\caption[Cr obesity associated metagene in \acrshort{icgc} \acrshort{blca} data]{Heatmap, box plot and scatter plot showing the association of Cr obesity associated metagene with sample gene expression, \gls{bmi} and \gls{bmi} status from \acrshort{icgc} \acrshort{blca} data, respectively.
	The results for other metagenes and other cancer types are in \cref{app:a}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:degmetaicgc}
\end{figure}

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cris_crdeg_trans_meta}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cris_crdeg_trans_meta}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cris_crdeg_trans_meta}
	\caption[Cr obesity associated metagene in \gls{nzbc} data]{Heatmap, box plot and scatter plot showing the association of Cr obesity associated metagene with sample gene expression, \gls{bmi} and \gls{bmi} status from \gls{nzbc} data, respectively.
	The results for other metagenes are in \cref{app:a}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:degmetaprint}
\end{figure}

@@

\begin{table}[htbp]
	\centering
	\caption{Summary of the number of \glspl{deg} identified in each \gls{icgc} cancer data set}
	\label{tab:icgcdegnum}
	\begin{tabular}{lc}
		Cancer type & No. of \glspl{deg} identified\\
		\hline
		\hline
		\rule{0pt}{2.25ex}\gls{blca} & 679 \\
		\gls{cesc} & 1229\\
		\gls{coad} & 974\\
		\gls{kirp} & 687\\
		\gls{lihc} & 3340\\
		\gls{read} & 796\\
		\gls{skcm} & 1137\\
		\gls{ucec} & 2934\\
		\hline
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[htbp]
	\centering
	\begin{threeparttable}
		\caption{Summary of the number of \glspl{deg} identified by the gene expression analysis and simulation analysis in \gls{icgc} cancer data}
		\label{tab:icgcdegtab}
		\begin{tabular}{>{\quad}lcccccccc}
			& \multicolumn{8}{c}{\small No. of cancer types expressing the \glspl{deg}\tnote{1}}\\
			& 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
			\hline
			\hline
			\rule{0pt}{2.25ex}\hspace{-1em}{\small Results from gene expression analysis} & 7330 & 2024 & 320 & 21 & 0 & 0 & 0 & 0 \\
			\hspace{-1em}{\small Results from simulation:\tnote{2}}                       &      &      &     &    &   &   &   &   \\
			{\small Mean no. of \glspl{deg} identified}                                   & 5732 & 1057 & 111 & 7  & 0 & 0 & 0 & 0 \\
			{\small $95^{th}$ percentile}                                                 & 6965 & 1722 & 227 & 20 & 2 & 0 & 0 & 0 \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\begin{footnotesize}
			\item [1] The numbers represent the number of cancer types a gene was expressed in.
			\item [2] The simulation was repeated 1000 times, each with randomised samples.
			\end{footnotesize}
		\end{tablenotes}
	\end{threeparttable}
\end{table}

>>>>

\begin{figure}[htb]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/creighton_mg_heatmap1}
	\caption[Obesity metagene from \citet{Creighton2012} study and sample gene expression in CR data] {Heatmap showing the obesity metagene from the \citet{Creighton2012} study with the sample gene expressions of the obesity associated genes in the CR data.
	Level of expression is represented in the top right histogram, where low and high gene expression are colour-coded with blue and red, respectively.
	Each row of the heatmap represents a gene from the obesity associated genetic signature, and each column of the heatmap represents a sample from the CR data.
	The obesity associated metagene scores of the samples are shown as a separate row at top of the heatmap, and the tree diagram of the heirarchical clustering of the genes is shown on the left of the heatmap.
	For clarity, the metagene scores were flipped in order to match the results from the \citet{Creighton2012} study.}
	\label{fig:crmetaheat}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=4,width=0.45\linewidth]{results1/creighton_mg_heatmap1}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/creighton_mg_heatmap1}
	\caption[Obesity metagene from the \citet{Creighton2012} study and sample \gls{bmi}/\gls{bmi} status in CR data]{Box plot and scatter plot showing the association of the obesity metagene from the \citet{Creighton2012} study with the sample \gls{bmi} status and \gls{bmi}, respectively, from the CR data.
	In the box plot, the p-values above the groups represent the statistical significance of the association of the obesity metagene with the overweight or obese group compared with the normal weight group.
	The \gls{anova} p-value shows the statistical significance of the association of the obesity metagene with the sample \gls{bmi} groups.
	In the scatter plot, $R^2$- and p-values describe the adjusted coefficient of determination of the regression line and the statistical significance of the linear model used to draw the regression line, respectively.}
	\label{fig:crmetaboxplot}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/crtcga_std}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/crtcga_std}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/crtcga_std}
	\caption[Obesity metagene from the \citet{Creighton2012} study in the \acrshort{icgc} \acrshort{blca} data]{Heatmap, box plot and scatter plot showing the association of the obesity metagene from the \citet{Creighton2012} study with the sample gene expression, \gls{bmi} and \gls{bmi} status, respectively, from the \gls{icgc} \gls{blca} data.
	The results for other \gls{icgc} cancer types are shown in \cref{sec:rest_of_the_cr_icgc_cancer_heatmap_results}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:crmetaicgc}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.8\linewidth,page=3]{results1/cris_cr_trans_meta}\\
	\vspace{1em}
	\includegraphics[width=0.45\linewidth,page=4]{results1/cris_cr_trans_meta}
	\hfill
	\includegraphics[width=0.45\linewidth,page=5]{results1/cris_cr_trans_meta}
	\caption[Obesity metagene from \citet{Creighton2012} study in the \gls{nzbc} data]{Heatmap, box plot and scatter plot showing the association of the obesity metagene from the \citet{Creighton2012} study with the sample gene expression, \gls{bmi} and \gls{bmi} status from the \gls{nzbc} data, respectively.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:crmetaprint}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cr_fm_meta}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cr_fm_meta}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cr_fm_meta}
	\caption[FM obesity metagene in the CR data]{Heatmap, box plot and scatter plot showing the association of the FM obesity associated metagene with the sample gene expression, \gls{bmi} and \gls{bmi} status from the CR  data, respectively.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:fmmetacr}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/fm_meta_ICGC}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/fm_meta_ICGC}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/fm_meta_ICGC}
	\caption[FM obesity metagene in the \acrshort{icgc} \acrshort{blca} data]{Heatmap, box plot and scatter plot showing the association of the FM obesity associated metagene with the sample gene expression, \gls{bmi} and \gls{bmi} status from the \acrshort{icgc} \acrshort{blca} data, respectively.
	The results for other \gls{icgc} cancer types are shown in \cref{sec:rest_of_the_fm_icgc_cancer_heatmap_results}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:fmmetaicgc}
\end{figure}

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cris_fm_meta}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cris_fm_meta}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cris_fm_meta}
	\caption[FM metagene in the \gls{nzbc} data]{Heatmap, box plot and scatter plot showing the association of the FM obesity associated metagene with the sample gene expression, \gls{bmi} and \gls{bmi} status from the \gls{nzbc} data, respectively.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:fmmetacris}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.5\linewidth]{results1/deg_venn1}
	\caption[Venn diagram of the \glspl{deg} identified from the CR data (all patients included)]{Venn diagram showing the common gene probes between the signatures obtained from the unadjusted and the clinical variable-adjusted CR data and the original obesity associated genetic signature. }
	\label{fig:venn1}
\end{figure}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.5\linewidth]{results1/deg_venn2}
	\caption[Venn diagram of the \glspl{deg} identified from the CR data (Caucasian patients only)]{Venn diagram showing the common gene probes between the signatures obtained from the unadjusted and the clinical variable-adjusted CR data (Caucasian patients only) and the original obesity associated genetic signature.}
	\label{fig:venn2}
\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption{Summary of the abbreviations used to refer to the different obesity associated genetic signatures identified in the CR data}
	\label{tab:mg_abbrev}
	\begin{tabular}{lp{0.51\textwidth}c}
		\hline
		\hline
		Abbreviation & Definition & No. of gene probes\\
		\hline
		\rule{0pt}{2.25ex}Or      & Original obesity associated genetic signature identified by \citet{Creighton2012}                       & 799\\
		\rule{0pt}{2.25ex}Cr      & Obesity associated genetic signature identified from unadjusted CR data                                & 799 \\
		\rule{0pt}{2.25ex}CrOl    & Genes common between Or and Cr genetic signatures                                                       & 239\\
		\rule{0pt}{2.25ex}Res     & Obesity associated genetic signature identified from clinical variable-adjusted CR data                & 799\\
		\rule{0pt}{2.25ex}ResOl   & Genes common between Or and Res genetic signatures                                                      & 168\\
		\rule{0pt}{2.25ex}Ca      & Obesity associated genetic signature identified from unadjusted Caucasian-only CR data                 & 799\\
		\rule{0pt}{2.25ex}CaOl    & Genes common between Or and Ca genetic signatures                                                       & 148\\
		\rule{0pt}{2.25ex}CaRes   & Obesity associated genetic signature identified from clinical variable-adjusted Caucasian-only CR data & 799\\
		\rule{0pt}{2.25ex}CaResOl & Genes common between Or and CaRes genetic signatures                                                    & 92\\
		\hline
		\hline
	\end{tabular}
\end{table}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cr_deg_meta_vs_clin}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cr_deg_meta_vs_clin}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cr_deg_meta_vs_clin}
	\caption[Cr obesity metagene in the CR data]{Heatmap, box plot and scatter plot showing the association of the Cr obesity associated metagene with the sample gene expression, \gls{bmi} and \gls{bmi} status from the CR data, respectively.
	The results for the other obesity metagenes are shown in \cref{sec:rest_of_the_cr_ob_meta_heatmap_results_cris}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:degmetacr}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.8\linewidth]{results1/cr_meta_cor}
	\caption[Pearson correlation of all eight obesity metagenes identified in the CR data]{Heatmap showing the Pearson correlation of all eight obesity associated metagenes from the CR data with one another.
	\gls{svd} was applied to the \gls{rma}-normalised CR data to generate each of the eight metagenes.
	High and low correlation were represented as red and blue, respectively, where the colours were matched with the values on the scale shown in the top right histogram.}
	\label{fig:cr_meta_cor}
\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes with the sample \gls{bmi}/\gls{bmi} status in the \gls{icgc} \gls{blca} cancer data}
	\label{tab:degmetablca}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			 Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr & {\bfseries 0.0134}\tnote{1} & 0.1365 & {\bfseries 0.0387} & 0.0171 & {\bfseries 0.0195} \\
			Res                  & {\bfseries 0.0055}          & 0.1974 & {\bfseries 0.0196} & 0.0117 & {\bfseries 0.0446} \\
			CrOl                 & {\bfseries 0.0383}          & 0.4583 & 0.1096             & 0.0047 & 0.1374             \\
			ResOl                & 0.0909                      & 0.7092 & 0.2125             & 0.0018 & 0.2254             \\
			Ca                   & {\bfseries 0.0077}          & 0.1973 & {\bfseries 0.0231} & 0.0116 & {\bfseries 0.0456} \\
			CaRes                & {\bfseries 0.0104}          & 0.2712 & {\bfseries 0.0322} & 0.0101 & 0.0572             \\
			CaOl                 & 0.0575                      & 0.6185 & 0.1487             & 0.0022 & 0.2126             \\
			CaResOl              & {\bfseries 0.0463}          & 0.5820 & 0.1263             & 0.0036 & 0.1660             \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/rawobsgene_ICGC}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/rawobsgene_ICGC}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/rawobsgene_ICGC}
	\caption[Cr obesity metagene in the \acrshort{icgc} \acrshort{blca} data]{Heatmap, box plot and scatter plot showing the association of the Cr obesity metagene with the sample gene expression, \gls{bmi} and \gls{bmi} status from the \acrshort{icgc} \acrshort{blca} data, respectively.
	The results for other other metagenes and other \gls{icgc} cancer types are shown in \cref{sec:rest_of_the_cr_icgc_cancer_heatmap_results}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:degmetaicgc}
\end{figure}

\begin{figure}[htp!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/cris_crdeg_trans_meta}\\
	\vspace{1em}
	\includegraphics[page=4,width=0.45\linewidth]{results1/cris_crdeg_trans_meta}
	\hfill
	\includegraphics[page=5,width=0.45\linewidth]{results1/cris_crdeg_trans_meta}
	\caption[Cr obesity metagene in the \gls{nzbc} data]{Heatmap, box plot and scatter plot showing the association of the Cr obesity associated metagene with the sample gene expression, \gls{bmi} and \gls{bmi} status from the \gls{nzbc} data, respectively.
	The results for the other obesity metagenes are shown in \cref{sec:rest_of_the_cr_ob_meta_heatmap_results_cris}.
	Scales, p-values and $R^2$-value are as described in previous figures.}
	\label{fig:degmetaprint}
\end{figure}

@@

\begin{table}[htbp]
	\centering
	\caption{Summary of the number of \glspl{deg} identified in each of the \gls{icgc} cancer data set}
	\label{tab:icgcdegnum}
	\begin{tabular}{lc}
		Cancer type & No. of \glspl{deg} identified\\
		\hline
		\hline
		\rule{0pt}{2.25ex}\gls{blca} & 679 \\
		\gls{cesc} & 1229\\
		\gls{coad} & 974\\
		\gls{kirp} & 687\\
		\gls{lihc} & 3340\\
		\gls{read} & 796\\
		\gls{skcm} & 1137\\
		\gls{ucec} & 2934\\
		\hline
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[htbp]
	\centering
	\begin{threeparttable}
		\caption{Summary of the number of \glspl{deg} identified by the gene expression analysis and simulation analysis in the \gls{icgc} cancer data}
		\label{tab:icgcdegtab}
		\begin{tabular}{>{\quad}lcccccccc}
			& \multicolumn{8}{c}{\small No. of cancer types expressing the \glspl{deg}\tnote{1}}\\
			& 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
			\hline
			\hline
			\rule{0pt}{2.25ex}\hspace{-1em}{\small Results from gene expression analysis} & 7330 & 2024 & 320 & 21 & 0 & 0 & 0 & 0 \\
			\hspace{-1em}{\small Results from simulation:\tnote{2}}                       &      &      &     &    &   &   &   &   \\
			{\small Mean no. of \glspl{deg} identified}                                   & 5732 & 1057 & 111 & 7  & 0 & 0 & 0 & 0 \\
			{\small $95^{th}$ percentile}                                                 & 6965 & 1722 & 227 & 20 & 2 & 0 & 0 & 0 \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\begin{footnotesize}
			\item [1] The numbers represent the number of cancer types a gene was expressed in.
			\item [2] The simulation was repeated 1000 times, each with randomised samples.
			\end{footnotesize}
		\end{tablenotes}
	\end{threeparttable}
\end{table}
